dbRDA analysis

### 2017-04-27 doc/RMD/RDA-analysis.Rmd
add some text
add session info

@@

>>>>

Out of both of the models, only Region explains the most variance, almost double
that of Host or Year and Severity contributes almost nothing.

@@

```{r, echo = FALSE, results = "asis"}
options(width = 100)
cat("<details><summary>Session Information</summary>\n```\n")
devtools::session_info()
cat("```\n</details>")
```
